Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-07-01 analysis/Study1.qmd
updated EGA andEFA analysis
removed item

@@

make_egas <- function(data) {
  egas <- list()
  for (model in c("glasso")) {  # , "TMFG"
    for (algo in c("walktrap", "louvain")) {
      for (type in c("ega", "ega.fit")) { # "" # "hierega"
        if (type == "ega.fit" & algo == "louvain") next # Too slow
        egas[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
          data = data,
          seed = 123,
          model = model,
          algorithm = algo,
          EGA.type = type,
          type = "resampling",
          plot.itemStability = FALSE,
          verbose = FALSE
        )
      }
    }
  }

@@

egas_all <- make_egas(data_all)
egas_all$p
```

@@

```{r}
n <- parameters::n_factors(data_all, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data1a, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data1b, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data2, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data3, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data4, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data5, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data6, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data7a, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data7b, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data7c, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data8a, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data8b, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data9, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data10a, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data10b, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data10c, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data11a, n_max = 12)

@@

```{r}
n <- parameters::n_factors(data11b, n_max = 12)

@@

efa5 <- parameters::factor_analysis(data_all, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa5)

@@

efa4 <- parameters::factor_analysis(data1a, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data1b, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data2, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data3, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data4, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data5, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data6, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data7a, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data7b, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data7c, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data8a, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data8b, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data9, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data10a, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data10b, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data10c, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data11a, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data11b, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

We discarded the following items:
- Tickle: not present in the same dataset and consistently flagged as redundant.
<!-- - Blood_Sugar -->

Ambiguous:
- Temp
- Vomit
- Affective_touch
- Sex_arousal
- Taste

>>>>

Discarded the following items:
- Tickle: not present in the same dataset and consistently flagged as redundant in UVA analysis.

Ambiguous:
- Temp
- Vomit
- Affective_touch
- Sex_arousal
- Taste
- Blood Sugar

@@

make_egas <- function(data) {
  egas <- list()
  for (model in c("glasso")) {  # , "TMFG"
    for (algo in c("walktrap", "louvain")) {
      for (type in c("ega", "ega.fit")) { # "" # "hierega"
        if (type == "ega.fit" & algo == "louvain") next # Too slow
        egas[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
          data = data,
          seed = 123,
          model = model,
          algorithm = algo,
          EGA.type = type,
          type = "resampling",
          plot.itemStability = FALSE,
          verbose = FALSE, 
        )
      }
    }
  }

@@

egas_all <- make_egas(data_all)
egas_all$p

@@

We discarded the following items: 
- Tickle
- Blood Sugar
- Temp
- Vomit
- Affective_touch
- Sex_arousal
- Taste

```{r}
cols_to_remove <- c("Temp", "Vomit", "Affective_touch", "Sex_arousal", "Taste", "Tickle", "Bloo")
```

```{r}
data_all <- data_all |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data_all, n_max = 12)

@@

```{r}
data1a <- data1a |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data1a, n_max = 12)

@@

```{r}
data1b <- data1b |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data1b, n_max = 12)

@@

```{r}
data2 <- data2 |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data2, n_max = 12)

@@

```{r}
data3 <- data3 |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data3, n_max = 12)

@@

```{r}
data4 <- data4 |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data4, n_max = 12)

@@

```{r}
data5 <- data5 |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data5, n_max = 12)

@@

```{r}
data6 <- data6 |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data6, n_max = 12)

@@

```{r}
data7a <- data7a |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data7a, n_max = 12)

@@

```{r}
data7b <- data7b |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data7b, n_max = 12)

@@

```{r}
data7c <- data7c |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data7c, n_max = 12)

@@

```{r}
data8a <- data8a |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data8a, n_max = 12)

@@

```{r}
data8b <- data8b |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data8b, n_max = 12)

@@

```{r}
data9 <- data9 |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data9, n_max = 12)

@@

```{r}
data10a <- data10a |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data10a, n_max = 12)

@@

```{r}
data10b <- data10b |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data10b, n_max = 12)

@@

```{r}
data10c <- data10c |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data10c, n_max = 12)

@@

```{r}
data11a <- data11a |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data11a, n_max = 12)

@@

```{r}
data11b <- data11b |>
  select(-any_of(cols_to_remove))

n <- parameters::n_factors(data11b, n_max = 12)

@@

efa5 <- parameters::factor_analysis(data_all, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa5)

@@

efa4 <- parameters::factor_analysis(data1a, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data1b, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data2, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data3, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data4, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data5, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data6, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data7a, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data7b, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data7c, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data8a, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data8b, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data9, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data10a, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data10b, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data10c, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data11a, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data11b, n = 3, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

We discarded the following items: 
- Tickle
- Blood Sugar
- Temp
- Vomit
- Affective_touch
- Sex_arousal
- Taste
